---
title: "Dominance Through the Lens of a Competitive Worldview"
subtitle: "Study 1: Analysis Report"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
knit: (function(input_file, encoding) { rmarkdown::render(input_file, encoding = encoding, output_file = 'index.html', output_dir = here::here('docs','studies','study-1')); })
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r,include=FALSE}
library(apa)
library(see)
library(lme4)
library(lmerTest)
library(interactions)
library(jtools)
library(gridExtra)
library(kableExtra)
library(apaTables)
library(papaja)
library(knitr)
library(psych)
library(GPArotation)
library(PerformanceAnalytics)
library(gt)
library(tidytext)
library(textdata)
library(tidyverse)
library(diagram)
library(factoextra)
library(SnowballC)
library(hunspell)
library(quanteda)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/dominance-in-the-competitive-jungle/main/study-1/data/"

df_s1 <- readr::read_csv(paste0(repo_url,"df_s1.csv"), show_col_types = FALSE)
```

```{r,include=FALSE}
df_s1 <- df_s1 %>% 
    mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu),
         white = ifelse(race == "white",1,0),
         man = ifelse(gender == "man",1,0))

df_s1_elg <- df_s1 %>% 
  filter(elg == 1)
```

# Background

The purpose of Study 1 is to provide discriminant and internal validity to our theoretical model: Those with a competitive worldview expect dominance to incur less relationship harm and, in turn, they are more likely to behave dominantly.

We want to make sure the design properly addresses the following:

  1. Competitive worldview, relationship expectancies of dominance, and dominance are all measured correctly. To that end, we only use well-validated scales:
    a. Competitive worldview: a view of the social world as a constant battle for status and resources (*It's a dog-eat-dog world where you have to be ruthless at times*; <a href="https://doi.org/10.1016/j.jrp.2012.10.004" target="_blank"> Perry et al., 2013</a>).
    b. Dominance strategies: use of dominant strategies at attain and maintain status at work (*I am willing to use aggressive tactics to get my way at work*; <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>).
    c. Relationship expectancies of dominance strategies: the same behaviors of the dominance strategies scale were assessed for their perceived impact on relationships with others at work. 
  2. It is competitive worldview that predicts relationship expectancies and dominance, over and above related constructs (that have been shown in the past to predict dominance). Therefore, we statistically control for the following: 
    a. Status zero-sum beliefs: the belief that if one gains status, others lose status (<a href="https://doi.org/10.1037/xge0001282" target="_blank"> Andrews-Fearon & Davidai, 2023</a>).
    b. Cooperative primal beliefs: the belief that people are naturally and inherently cooperative (<a href="https://doi.org/10.1037/pas0000639" target="_blank"> Clifton et al., 2019</a>).
    c. Coercive theories power: lay theories according to which the way to maintain power is through coercion, intimidation, and force (<a href="https://doi.org/10.1037/pspi0000345" target="_blank"> ten Brinke & Keltner, 2022</a>).
    d. Collaborative theories of power: lay theories according to which the way to maintain power is through virtue, respect, and empathy (<a href="https://doi.org/10.1037/pspi0000345" target="_blank"> ten Brinke & Keltner, 2022</a>).
  3. It is relationship expectancies, and not relationship motivations or influence expectancies, that is driving the effect of competitive worldview on dominance strategies at work. To that end, we measure:
    a. Relationship motivations: two items measuring the extent to which participants care about having good relationships at work.
    b. Influence expectancies of dominance strategies: the same behaviors of the dominance strategies scale were assessed for their perceived impact on influence over others at work.
    
We also want to be able to ask about people's daily lives, so we limit our sample to full- and part-time employees.

# Preregistered hypotheses

This study was preregistered here: <a href="https://osf.io/ygs53/?view_only=f5844a8417ec4ce8ae1c45e8cd858674" target="_blank"> Open Science Framework</a>

  1. Competitive worldview will be positively associated with self-reported dominance strategies.
  2. Competitive worldview will be positively associated with relationship expectancies of dominance strategies.
  3. The relationship between competitive worldview and self dominance strategies will be–at least partially–explained by relationship expectancies of dominance strategies.

# Data collection

We collected data on Jan. 27th, 2024 through Connect by CloudResearch; an online participant recruitment platform. We restricted our sample to full- and part-time employees. The target sample was set at 300 participants, lending us sufficient statistical power to find our hypothesized effect.\
\
We excluded participants who failed two preregistered attention checks, as well as those who got through the platforms filter despite not being full- or part-time employes.

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
n_eligible <- df_s1 %>% 
  group_by(elg) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  filter(elg == 1) %>% 
  select(N) %>% 
  unlist() %>% 
  unname()

passed_checks <- df_s1 %>% 
  group_by(att_1,att_2) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  filter(att_1 == 1 & att_2 == 1) %>% 
  select(N) %>% 
  unlist() %>% 
  unname()

df_s1 %>% 
  group_by(att_1,att_2) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

`r passed_checks` participants passed both attention checks.

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s1 %>% 
  filter(att_1 == 1 & att_2 == 1) %>% 
  group_by(employment) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

4 are not longer employed.

That leaves us with `r n_eligible` eligible participants.

# Demographics

## Race/Ethnicity

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s1_elg %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s1_elg %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s1_elg %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s1_elg %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
median_income_num <- df_s1_elg %>% 
  summarise(median = median(income_num,na.rm = T))

median_income <- median_income_num %>% 
  mutate(income_char = case_when(median == 1 ~ "$0-$20,000",
                                 median == 2 ~ "$20,001-$40,000",
                                 median == 3 ~ "$40,001-$60,000",
                                 median == 4 ~ "$60,001-$80,000",
                                 median == 5 ~ "$80,001-$100,000",
                                 median == 6 ~ "$100,001-$120,000",
                                 median == 7 ~ "$120,001-$140,000",
                                 median == 8 ~ "$140,001-$160,000",
                                 median == 9 ~ "$160,001-$180,000",
                                 median == 10 ~ "$180,001-$200,000",
                                 median == 11 ~ "Over $200,000")) %>% 
  select(income_char) %>% 
  unlist() %>% 
  unname()

df_s1_elg %>%
  ggplot(aes(x = income, fill = income == median_income)) +
  geom_bar(show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey66", "TRUE" = "red")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

Median income: **`r median_income`**.

# Primary Measures

## Competitive worldview

```{r,include=F}
alpha_score <- df_s1_elg %>% 
  dplyr::select(CWV_1:CWV_10R) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1016/j.jrp.2012.10.004" target="_blank"> Perry et al., 2013</a>

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. It’s a dog-eat-dog world where you have to be ruthless at times
  2. Life is not governed by the "survival of the fittest." We should let compassion and moral laws be our guide [R]
  3. There is really no such thing as "right" and "wrong." It all boils down to what you can get away with
  4. One of the most useful skills a person should develop is how to look someone straight in the eye and lie convincingly
  5. It is better to be loved than to be feared [R]
  6. My knowledge and experience tell me that the social world we live in is basically a competitive "jungle" in which the fittest survive and succeed, in which power, wealth, and winning are everything, and might is right
  7. Do unto others as you would have them do unto you, and never do anything unfair to someone else [R]
  8. Basically people are objects to be quietly and coolly manipulated for one’s own benefit
  9. Honesty is the best policy in all cases [R]
  10. One should give others the benefit of the doubt. Most people are trustworthy if you have faith in them [R]

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = CWV)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$CWV,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Cooperative primal beliefs

```{r,include=F}
alpha_score <- df_s1_elg %>% 
  dplyr::select(copri_1R:copri_4) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1037/pas0000639" target="_blank"> Clifton et al., 2019</a>

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. For all life—from the smallest organisms, to plants, animals, and for people too—everything is a cut-throat competition [R]
  2. Instead of being cooperative, life is a brutal contest where you’ve got to do whatever it takes to survive [R]
  3. Instead of being cooperative, the world is a cut-throat and competitive place [R]
  4. The world runs on trust and cooperation way more than suspicion and competition

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = copri)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$copri,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Status zero-sum beliefs

```{r,include=F}
alpha_score <- df_s1_elg %>% 
  dplyr::select(ZSB_1:ZSB_8R) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1037/xge0001282" target="_blank"> Andrews-Fearon & Davidai, 2023</a>

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. When status for one person is increasing it means that status for another person is decreasing
  2. Status is a limited good—when one person gains in status it inevitably comes at another person’s expense
  3. When one person moves up the social hierarchy it means that another person has to move down the hierarchy
  4. If someone wants to move up the social hierarchy, they have to do so at someone else’s expense
  5. Status is not a finite resource [R]
  6. When one person has a lot of status it doesn’t mean that someone else lacks status [R]
  7. Not everyone can be high status. If one person has higher status, someone else must have lower status
  8. When one person gains in status, it does not mean that someone else is losing status [R]

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = ZSB)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$ZSB,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Coercive theories of power

```{r,include=F}
alpha_score <- df_s1_elg %>% 
  dplyr::select(TOPS_coer_1:TOPS_coer_10) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1037/pspi0000345" target="_blank"> ten Brinke & Keltner, 2022</a>

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. Maintaining power requires ruthlessness
  2. People keep power by being feared by others
  3. People gain power through the use of manipulation and deception
  4. People mainly gain power by force
  5. To maintain power, a person must be willing to do whatever is necessary, including breaking the rules, using force, and coercion
  6. People most typically gain power by reducing the status of other people
  7. Often it requires aggression to gain power
  8. An influential individual is typically intimidating
  9. Having power means always having the "final say"
  10. Power is usually vertically arranged, with a few people at the top having most of the influence and many at the bottom having little to none

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = TOPS_coer)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$TOPS_coer,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Collaborative theories of power

```{r,include=F}
alpha_score <- df_s1_elg %>% 
  dplyr::select(TOPS_coll_1:TOPS_coll_10) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1037/pspi0000345" target="_blank"> ten Brinke & Keltner, 2022</a>

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. Maintaining power requires the ability to collaborate and compromise with others
  2. Maintaining power requires compassion for others
  3. People rise in power through virtue and respect
  4. Having high ethical and moral standards is necessary to keep power
  5. Powerful individuals focus on the needs of group members
  6. Influential individuals need to be approachable and empathetic
  7. Gaining power requires collaboration with other individuals
  8. People most typically gain power by being given responsibilities and opportunities by others
  9. In a group, there can be many influential people
  10. Power is often shared by many individuals in a group

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = TOPS_coll)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$TOPS_coll,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Dominance strategies

```{r,include=F}
alpha_score <- df_s1_elg %>%
  dplyr::select(self_2,
                self_4,
                self_6,
                self_8,
                self_9R,
                self_11,
                self_12R,
                self_14,
                self_16) %>%
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>

We're now going to shift to some of your other experiences at work.

Please indicate the extent to which each statement below accurately describes you at work, using any of the points on the 7 point scale...

1 = *Not at all* to 7 = *Very much*

  1. I enjoy (or would enjoy) having control over others at work
  2. I often try to get my own way at work regardless of what others may want
  3. I am willing to use aggressive tactics to get my way at work
  4. I try to control others rather than permit them to control me at work
  5. I do NOT have a forceful or dominant personality at work [R]
  6. Others know it is better to let me have my way at work
  7. I do NOT enjoying having authority over other people at work [R]
  8. Some people at work are afraid of me
  9. Others at work do NOT enjoying hanging out with me

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = self_dominance)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$self_dominance,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Relationship expectancies of dominance

```{r,include=F}
alpha_score <- df_s1_elg %>%
  dplyr::select(exp_rel_2,
         exp_rel_4,
         exp_rel_6,
         exp_rel_8,
         exp_rel_9R,
         exp_rel_11,
         exp_rel_12R,
         exp_rel_14,
         exp_rel_16) %>%
  psych::alpha()

alpha <- alpha_score$total[1]
```

Adapted from <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>

What leads someone to have good **relationships?**

Below, we list some attributes and behaviors that a person might display in a group of other people. What do you think is the impact of each of these things on whether that person **has good relationships with others in that group?**

1 = *Strong negative effect on relationships* to 7 = *Strong positive effect on relationships*

  1. Enjoying having control over other members of the group
  2. Often trying to get their own way regardless of what others in the group may want
  3. Being willing to use aggressive tactics to get their way
  4. Trying to control others rather than permit others to control them
  5. NOT having a forceful or dominant personality [R]
  6. Having members of the group know it is better to let him/her have his/her way
  7. NOT enjoying having authority over other members of the group [R]
  8. Having members of their group being afraid of them
  9. Others NOT enjoying hanging out with them

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = rel_dominance)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$rel_dominance,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Influence expectancies of dominance

```{r,include=F}
alpha_score <- df_s1_elg %>%
  dplyr::select(exp_infl_2,
         exp_infl_4,
         exp_infl_6,
         exp_infl_8,
         exp_infl_9R,
         exp_infl_11,
         exp_infl_12R,
         exp_infl_14,
         exp_infl_16) %>%
  psych::alpha()

alpha <- alpha_score$total[1]
```

Adapted from <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>

What leads someone to have **influence?**

Below, we list some attributes and behaviors that a person might display in a group of other people. What do you think is the impact of each of these things on whether that person **has influence over others in that group?**

1 = *Strong negative effect on influence* to 7 = *Strong positive effect on influence*

  1. Enjoying having control over other members of the group
  2. Often trying to get their own way regardless of what others in the group may want
  3. Being willing to use aggressive tactics to get their way
  4. Trying to control others rather than permit others to control them
  5. NOT having a forceful or dominant personality [R]
  6. Having members of the group know it is better to let him/her have his/her way
  7. NOT enjoying having authority over other members of the group [R]
  8. Having members of their group being afraid of them
  9. Others NOT enjoying hanging out with them

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = infl_dominance)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$infl_dominance,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Relationship motivations at work

Mean score of the following two items:

  1. In your work life, to what extent do you care about having good relationships with the people you work with? (1 = *I don't care about this at all* to 5 = *I care about this a great deal*)
  2. In your work life, to what extent would it bother you if you did NOT have good relationships with other people at work? (1 = *I would not be bothered at all if I didn't have good relationships* to 5 = *I would be greatly bothered if I didn't have good relationships*)

```{r,include=FALSE}
cormat <- df_s1_elg %>% 
  dplyr::select(rel_care,rel_bother) %>% 
  cor()

correlation = cormat[1,2]
```

*r* = `r round(correlation,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = care_rel)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,5,1),
                     limits = c(1,5)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$care_rel,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

# Additional measures

## Prestige strategies

```{r,include=F}
alpha_score <- df_s1_elg %>%
  dplyr::select(self_1,
         self_3,
         self_5R,
         self_7,
         self_10,
         self_13,
         self_15) %>%
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>

We're now going to shift to some of your other experiences at work.

Please indicate the extent to which each statement below accurately describes you at work, using any of the points on the 7 point scale...

1 = *Not at all* to 7 = *Very much*

  1. My peers at work respect and admire me
  2. Others at work always expect me to be successful
  3. Others do NOT value my opinion at work [R]
  4. I am held in high esteem by those I know at work
  5. I am considered an expert on some matters by others at work
  6. My unique talents and abilities are recognized by others at work
  7. Others seek my advice on a variety of matters at work

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = self_prestige)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$self_prestige,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Relationship expectancies of prestige

```{r,include=F}
alpha_score <- df_s1_elg %>%
  dplyr::select(exp_rel_1,
         exp_rel_3,
         exp_rel_5R,
         exp_rel_7,
         exp_rel_10,
         exp_rel_13,
         exp_rel_15) %>%
  psych::alpha()

alpha <- alpha_score$total[1]
```

Adapted from <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>

What leads someone to have good **relationships?**

Below, we list some attributes and behaviors that a person might display in a group of other people. What do you think is the impact of each of these things on whether that person **has good relationships with others in that group?**

1 = *Strong negative effect on relationships* to 7 = *Strong positive effect on relationships*

  1. Having members of their group respect and admire them
  2. Having members of their group always expect him/her to be successful.
  3. Having members of their group do NOT value their opinion [R]
  4. Being held in high esteem by members of the group
  5. Being considered an expert on some matters by members of the group
  6. Having their unique talents and abilities are recognized by others in the group
  7. Having members of their group seek their advice on a variety of matters

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = rel_prestige)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$rel_prestige,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Influence expectancies of prestige

```{r,include=F}
alpha_score <- df_s1_elg %>%
  dplyr::select(exp_infl_1,
         exp_infl_3,
         exp_infl_5R,
         exp_infl_7,
         exp_infl_10,
         exp_infl_13,
         exp_infl_15) %>%
  psych::alpha()

alpha <- alpha_score$total[1]
```

Adapted from <a href="https://doi.org/10.1016/j.evolhumbehav.2010.02.004" target="_blank"> Cheng et al., 2010</a>

What leads someone to have **influence?**

Below, we list some attributes and behaviors that a person might display in a group of other people. What do you think is the impact of each of these things on whether that person **has influence over others in that group?**

1 = *Strong negative effect on influence* to 7 = *Strong positive effect on influence*

  1. Having members of their group respect and admire them
  2. Having members of their group always expect him/her to be successful.
  3. Having members of their group do NOT value their opinion [R]
  4. Being held in high esteem by members of the group
  5. Being considered an expert on some matters by members of the group
  6. Having their unique talents and abilities are recognized by others in the group
  7. Having members of their group seek their advice on a variety of matters

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = infl_prestige)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$infl_prestige,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Influence motivations at work

Mean score of the following two items:

  1. In your work life, to what extent do you care about having influence over the people you work with? (1 = *I don't care about having influence at all* to 5 = *I care about having influence a great deal*)
  2. In your work life, to what extent would it bother you if you did NOT have much influence of other people at work? (1 = *I would not be bothered at all if I didn't have influence* to 5 = *I would be greatly bothered if I didn't have influence*)

```{r,include=FALSE}
cormat <- df_s1_elg %>% 
  dplyr::select(infl_care,infl_bother) %>% 
  cor()

correlation = cormat[1,2]
```

*r* = `r round(correlation,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s1_elg %>% 
  ggplot(aes(x = care_infl)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,5,1),
                     limits = c(1,5)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s1_elg$care_infl,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

# Correlations

<a href="./app/index.html" target="_blank" rel="noopener"
     style="background:#0b69ff;color:white;padding:0.55em 0.9em;border-radius:8px;text-decoration:none;">
    EXPLORE CORRELATIONS ↗
  </a>

**Key:**

  1. CWV: Competitive worldview
  2. ZSB: Zero-sum beliefs
  3. copri: Cooperaitve primal beliefs
  4. self_dominance: Dominance strategies
  5. self_prestige: Prestige strategies
  6. rel_dominance: Relationship expectancies of dominance
  7. rel_prestige: Relationship expectancies of prestige
  8. infl_dominance: Influence expectancies of dominance
  9. infl_prestige: Influence expectancies of prestige
  10. TOPS_coer: Coercive theories of power
  11. TOPS_coll: Collaborative theories of power
  12. care_rel: Relationship motivations at work
  13. care_infl: Influence motivations at work

```{r,fig.align='left',echo=TRUE,warning=FALSE,message=FALSE,fig.dim=c(9,9)}
df_s1_elg %>% 
  dplyr::select(CWV,
                ZSB,
                copri,
                self_dominance,
                self_prestige,
                rel_dominance,
                rel_prestige,
                infl_dominance,
                infl_prestige,
                TOPS_coer,
                TOPS_coll,
                care_rel,
                care_infl) %>%
  corPlot(upper = TRUE,stars = TRUE,xsrt = 270)
```
