---
title: "Dominance Through the Lens of a Competitive Worldview"
subtitle: "Study 3A: Analysis Report"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
knit: (function(input_file, encoding) { rmarkdown::render(input_file, encoding = encoding, output_file = 'index.html', output_dir = here::here('docs','studies','study-3a')); })
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r,include=FALSE}
library(apa)
library(see)
library(lme4)
library(lmerTest)
library(interactions)
library(jtools)
library(gridExtra)
library(kableExtra)
library(apaTables)
library(papaja)
library(knitr)
library(psych)
library(GPArotation)
library(PerformanceAnalytics)
library(gt)
library(tidytext)
library(textdata)
library(tidyverse)
library(diagram)
library(factoextra)
library(SnowballC)
library(hunspell)
library(effectsize)
library(lavaan)
library(quanteda)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/dominance-in-the-competitive-jungle/main/study-3a/data/"

df_s3a_employees <- readr::read_csv(paste0(repo_url,"df_s3a_employees.csv"), show_col_types = FALSE)
df_s3a_managers <- readr::read_csv(paste0(repo_url,"df_s3a_managers.csv"), show_col_types = FALSE)

set.seed(20240914)
```

```{r,include=FALSE}
df_s3a_managers <- df_s3a_managers  %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu),
         man = ifelse(gender == "man",1,0),
         white = ifelse(race == "white",1,0)) %>% 
  mutate(is_dom = ifelse(message_choice == "dom",1,0))

df_s3a_employees <- df_s3a_employees %>% 
    mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu))
```


# Background

While Studies 1 and 2 supported our model, neither featured a behavioral measure of dominance. Study 3A sought such evidence with a novel paradigm, asking some participants to role-play as managers attempting to induce employees to complete a relatively unpleasant task and other participants to role-play as employees being induced to perform the task (a common dynamic in Study 2’s reports of real-world dominance). This paradigm allowed us to test again for the predictive role of competitive worldviews and relationship expectancies. Importantly, it also offered an empirical opportunity to evaluate errors in expectancies. Studies 1 and 2 do not shed light on whether, say, those with a competitive worldview are underestimating relationship costs of dominance or, alternatively, if those without a competitive worldview are overestimating such costs. The question remains: Are those high in competitive worldview or dominance overly optimistic or are those low in competitive worldview or dominance overly pessimistic about people’s responses to dominant behavior—or both? In the current study, we can assess this by comparing managerial predictions of relationship outcomes to employees’ actual behavior and self-reported attitudes towards their manager.

# Procedure

The study was conducted in two phases: One in which one sample of participants acted as managers and one in which another sample of participants acted as employees. Our design was informed by the behavioral reports gathered in Study 2, which tended to revolve around managers pressing employees to complete unpleasant work with some threat for noncompliance or underperformance. Phase 1 participants were asked to imagine that they were managers in a mid-sized company facing a tough task to be assigned to their employee—another participant on Connect by CloudResearch. The employee’s performance on the task determined the manager’s bonus (up to \$2 in addition to a base pay of \$1.60). The employee also had a \$2 “pending” bonus, but the amount they would receive would be determined by their manager (who could factor in the employee’s performance as much or little as they wanted). Importantly, these bonuses were independent: the amount awarded to the employee had no impact on the amount awarded to the manager. After receiving information about the task and bonus payment structure, manager participants were told that they could motivate their employees with one of two messages, one of which was dominant, and the other non-dominant. For each message, the managers predicted how well the employee would perform in the task and how the message would impact the employee’s attitude towards them. Then, the manager selected the message they wished to send to the employee. After selecting the message, they indicated if they believed the employee would nominate them for an additional paid “good manager” survey. Next, they indicated the bonus they wished to grant the employee for every possible level of performance in the task. Finally, they completed a measure of competitive worldview.

Phase 2 participants were asked to imagine that they were employees in a mid-sized firm. We informed them that they had been randomly assigned a manager who had participated in a previous phase of the study. After reading about the scenario, the task, and the bonus payment structure (where the manager’s bonus depended on their performance, but their own bonus was independent, decided solely by the manager), participants were told that the manager chose to send them a message. They then read the message that the manager selected to send (either dominant or non-dominant) and indicated if they wanted to complete the task. If not, they answered a number of questions about the manager and ended the survey at the agreed-upon \$0.80 base pay. If yes, they began a five-round task (described below). After completing the task, they saw their score, indicated their attitudes about the manager, and were asked if they would recommend the manager for a paid “good manager” follow-up study. Finally, they were told how much the manager decided to grant them out of the \$2 pending bonus. See Figure 3 for a visual description of the procedure.
 
# Preregistered hypotheses

This study was preregistered here: <a href="https://osf.io/8jzp5/overview?view_only=cbe1b5eb3a604f06b988ac9a3890053f" target="_blank">Open Science Framework</a>

  1. Managers’ competitive worldview will be associated with the belief that dominant behavior will harm the relationship with the employee less, rather than more. 
  2. Managers’ competitive worldview will be positively associated with choice to behave dominantly toward their employees.
  3. The relationship between managers’ competitive worldview and choice to behave dominantly will be at least partially explained by the expected impact of that dominant behavior on the relationship with the employee.
  
# Data collection

Participants were recruited through Connect by CloudResearch - an online participant pool.

## Phase 1 Participants (Managers)

```{r,echo=FALSE,results='asis',warning=FALSE,message=F}
total_n <- df_s3a_managers %>% 
  nrow()
```

Total N = **`r total_n`**.

```{r,echo=FALSE,results='asis',warning=FALSE,message=F}
df_s3a_managers_elg <- df_s3a_managers %>% 
  filter(elg == 1)

eligible_n = df_s3a_managers_elg %>% 
  nrow()
```

Eligible N = **`r eligible_n`**.

### Race/Ethnicity

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s3a_managers_elg %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s3a_managers_elg %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s3a_managers_elg %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s3a_managers_elg %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
median_income_num <- df_s3a_managers_elg %>% 
  summarise(median = median(income_num,na.rm = T))

median_income <- median_income_num %>% 
  mutate(income_char = case_when(median == 1 ~ "$0-$20,000",
                                 median == 2 ~ "$20,001-$40,000",
                                 median == 3 ~ "$40,001-$60,000",
                                 median == 4 ~ "$60,001-$80,000",
                                 median == 5 ~ "$80,001-$100,000",
                                 median == 6 ~ "$100,001-$120,000",
                                 median == 7 ~ "$120,001-$140,000",
                                 median == 8 ~ "$140,001-$160,000",
                                 median == 9 ~ "$160,001-$180,000",
                                 median == 10 ~ "$180,001-$200,000",
                                 median == 11 ~ "Over $200,000")) %>% 
  select(income_char) %>% 
  unlist() %>% 
  unname()

df_s3a_managers_elg %>%
  ggplot(aes(x = income, fill = income == median_income)) +
  geom_bar(show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey66", "TRUE" = "red")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

Median income: **`r median_income`**.

## Phase 2 Participants (Employees)

```{r,echo=FALSE,results='asis',warning=FALSE,message=F}
total_n <- df_s3a_managers %>% 
  nrow()
```

Total N = **`r total_n`**.

```{r,echo=FALSE,results='asis',warning=FALSE,message=F}
df_s3a_managers_elg <- df_s3a_managers %>% 
  filter(elg == 1)

eligible_n = df_s3a_managers_elg %>% 
  nrow()
```

Eligible N = **`r eligible_n`**.

### Race/Ethnicity

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s3a_managers_elg %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s3a_managers_elg %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s3a_managers_elg %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s3a_managers_elg %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
median_income_num <- df_s3a_managers_elg %>% 
  summarise(median = median(income_num,na.rm = T))

median_income <- median_income_num %>% 
  mutate(income_char = case_when(median == 1 ~ "$0-$20,000",
                                 median == 2 ~ "$20,001-$40,000",
                                 median == 3 ~ "$40,001-$60,000",
                                 median == 4 ~ "$60,001-$80,000",
                                 median == 5 ~ "$80,001-$100,000",
                                 median == 6 ~ "$100,001-$120,000",
                                 median == 7 ~ "$120,001-$140,000",
                                 median == 8 ~ "$140,001-$160,000",
                                 median == 9 ~ "$160,001-$180,000",
                                 median == 10 ~ "$180,001-$200,000",
                                 median == 11 ~ "Over $200,000")) %>% 
  select(income_char) %>% 
  unlist() %>% 
  unname()

df_s3a_managers_elg %>%
  ggplot(aes(x = income, fill = income == median_income)) +
  geom_bar(show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey66", "TRUE" = "red")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

Median income: **`r median_income`**.