---
title: "Dominance Through the Lens of a Competitive Worldview"
subtitle: "Study 2: Analysis Report"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
knit: (function(input_file, encoding) { rmarkdown::render(input_file, encoding = encoding, output_file = 'index.html', output_dir = here::here('docs','studies','study-2')); })
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r,include=FALSE}
library(apa)
library(see)
library(lme4)
library(lmerTest)
library(interactions)
library(jtools)
library(gridExtra)
library(kableExtra)
library(apaTables)
library(papaja)
library(knitr)
library(psych)
library(GPArotation)
library(PerformanceAnalytics)
library(gt)
library(tidytext)
library(textdata)
library(tidyverse)
library(diagram)
library(factoextra)
library(SnowballC)
library(hunspell)
library(effectsize)
library(lavaan)
library(quanteda)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/dominance-in-the-competitive-jungle/main/study-2/data/"

df_s2 <- readr::read_csv(paste0(repo_url,"df_s2.csv"), show_col_types = FALSE)
s2_descriptions <- readr::read_csv(paste0(repo_url,"s2-descriptions.csv"), show_col_types = FALSE)

set.seed(20240914)
```

```{r,include=FALSE}
df_s2 <- df_s2 %>% 
    mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu),
         white = ifelse(race == "white",1,0),
         man = ifelse(gender == "man",1,0))

df_s2_elg <- df_s2 %>% 
  filter(elg == 1)
```

# Background

The purpose of Study 2 was to test the external validity of our model. To that end, instead of relying on scales of dominant strategies at the workplace (as was done in Study 1), we crowd-sourced real-world instances of managerial dominance. So, we first asked full or part-time employees to recall a time in which they manager (or previous manager) behaved dominantly in order to induce compliance. We then pooled from those descriptions and asked participants to estimate the impact of that behavior on the relationship between the manager and employee. Then, participants indicated the extent to which they would have behaved dominantly if they were the manager in the same situation. 
 
# Preregistered hypotheses

This study was preregistered here: <a href="https://osf.io/493q6/?view_only=ba0c4d08a7344522b8d0ab2557ac4c07" target="_blank">Open Science Framework</a>

  1. Competitive worldview will be positively associated with perceived relational benefit from managers’ dominant behaviors (i.e., those higher in competitive worldview will perceive fewer relational costs to dominant behaviors).
  2. Competitive worldview will be positively associated with self-reported hypothetical dominant behavior as a manager.
  3. The relationship between competitive worldview and self-reported hypothetical dominant behavior as a manager will be at least partially explained by perceived relational benefit from dominant behaviors.

# Data collection

We collected descriptions of managerial dominance during March 2024. Then, after finalizing the pool of descriptions (23 total), we sampled 300 participants on Apr. 8th, 2024 through Connect by CloudResearch.

We excluded participants who failed one preregistered attention check, as well as those who got through the platforms filter despite not being full- or part-time employees.

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
n_eligible <- df_s2 %>% 
  group_by(elg) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  filter(elg == 1) %>% 
  select(N) %>% 
  unlist() %>% 
  unname()

passed_checks <- df_s2 %>% 
  group_by(att_1) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  filter(att_1 == 1) %>% 
  select(N) %>% 
  unlist() %>% 
  unname()

df_s2 %>% 
  group_by(att_1) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

`r passed_checks` participants passed both attention checks.

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s2 %>% 
  filter(att_1 == 1) %>% 
  group_by(employment) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

5 are no longer employed.

That leaves us with `r n_eligible` eligible participants.

# Demographics

## Race/Ethnicity

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s2_elg %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s2_elg %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s2_elg %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s2_elg %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
median_income_num <- df_s2_elg %>% 
  summarise(median = median(income_num,na.rm = T))

median_income <- median_income_num %>% 
  mutate(income_char = case_when(median == 1 ~ "$0-$20,000",
                                 median == 2 ~ "$20,001-$40,000",
                                 median == 3 ~ "$40,001-$60,000",
                                 median == 4 ~ "$60,001-$80,000",
                                 median == 5 ~ "$80,001-$100,000",
                                 median == 6 ~ "$100,001-$120,000",
                                 median == 7 ~ "$120,001-$140,000",
                                 median == 8 ~ "$140,001-$160,000",
                                 median == 9 ~ "$160,001-$180,000",
                                 median == 10 ~ "$180,001-$200,000",
                                 median == 11 ~ "Over $200,000")) %>% 
  select(income_char) %>% 
  unlist() %>% 
  unname()

df_s2_elg %>%
  ggplot(aes(x = income, fill = income == median_income)) +
  geom_bar(show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey66", "TRUE" = "red")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

Median income: **`r median_income`**.

# Descriptions of Managerial Dominance

Participants read one of the following descriptions:

```{r,echo=TRUE,results='asis',warning=FALSE}
s2_descriptions %>% 
  select(description) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                position = "left") %>% 
  scroll_box(width = "100%", height = "400px")

```

# Description-specific measures

They were asked the following questions about the randomly-selected description that they saw: open-ended reflection on the employee's reaction to the manager's behavior; the impact of the incident on the relationship with the manager; the impact of the incident on the employee's quitting intentions (as another operationalization of relationship impact); the extent to which the employee complied with what the manager was seeking; and how they would behave if they were the manager in a similar situation.

## Open-ended reactions

What do you think happened as a consequence to the manager's behavior? Please describe the
employee's reaction to it.


**50-character minimum*

**Paste disabled*

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s2_elg %>% 
  select(react) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                position = "left") %>% 
  scroll_box(width = "100%", height = "400px")
```

## Relationship impact

In your opinion, what was the impact of this incident on the employee's relationship with this manager? (1 = *It had a strong negative effect on their relationship with their manager* to 7 = *It had a strong positive effect on their relationship with their manager*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s2_elg %>% 
  ggplot(aes(x = impact_rel)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s2_elg$impact_rel,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Compliance impact

In your opinion, to what extent did the employee comply with what the manager was seeking or requesting? (1 = *They did not comply at all with what the manager was seeking* to 7 = *They completely complied with what the manager was seeking*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s2_elg %>% 
  ggplot(aes(x = impact_comp)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s2_elg$impact_comp,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Quitting intention impact

In your opinion, what was the impact of this incident on the employee's intentions to leave this manager or job (such as quitting or transferring)? (1 = *It greatly decreased their intentions to leave their manager* to 7 = *It greatly increased their intentions to leave their manager*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s2_elg %>% 
  ggplot(aes(x = impact_quit)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s2_elg$impact_quit,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Intentions of dominant behavior

In this situation, the manager wanted the employee to do something specific:

[TASK FROM MANAGER]. 

If you were a manager in this kind of situation, how likely would you be to act in the way the manager did, as described earlier? (1 = *Not at All Likely* to 5 = *Extremely Likely*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s2_elg %>% 
  ggplot(aes(x = own_likeman)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,5,1),
                     limits = c(0,6)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s2_elg$own_likeman,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Competitive worldview

They completed the Competitive Worldview scale at the end of the survey.

```{r,include=F}
alpha_score <- df_s2_elg %>% 
  dplyr::select(CWV_1:CWV_10R) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

From <a href="https://doi.org/10.1016/j.jrp.2012.10.004" target="_blank"> Perry et al., 2013</a>

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. It’s a dog-eat-dog world where you have to be ruthless at times
  2. Life is not governed by the "survival of the fittest." We should let compassion and moral laws be our guide [R]
  3. There is really no such thing as "right" and "wrong." It all boils down to what you can get away with
  4. One of the most useful skills a person should develop is how to look someone straight in the eye and lie convincingly
  5. It is better to be loved than to be feared [R]
  6. My knowledge and experience tell me that the social world we live in is basically a competitive "jungle" in which the fittest survive and succeed, in which power, wealth, and winning are everything, and might is right
  7. Do unto others as you would have them do unto you, and never do anything unfair to someone else [R]
  8. Basically people are objects to be quietly and coolly manipulated for one’s own benefit
  9. Honesty is the best policy in all cases [R]
  10. One should give others the benefit of the doubt. Most people are trustworthy if you have faith in them [R]

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s2_elg %>% 
  ggplot(aes(x = CWV)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s2_elg$CWV,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

# Linear Random Effects Models

## Linear Random Effects Model 1

**Predictor:** Competitive worldview.

**Outcome:** Dominant behavior (like the manager).

**Random effect:** Description.

**Controls:** Age, race (white = 1; non-white = 0), gender (man = 1; non-man = 0), education (numeric), income (numeric).

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}
m1 <- lmerTest::lmer(own_likeman ~ CWV + (1|og_pid) + age + white + man + edu_num + income_num,data = df_s2_elg)

eta_table <- eta_squared(m1)
etas_for_table <- c(NA,eta_table$Eta2_partial)
apa_lm <- apa_print(m1)
table_for_print <- apa_lm$table %>% 
  mutate(eta2 = round(etas_for_table,3))

kbl(table_for_print) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Linear Random Effects Model 2

**Predictor:** Competitive worldview.

**Outcome:** Predicted relationship impact.

**Random effect:** Description.

**Controls:** Age, race (white = 1; non-white = 0), gender (man = 1; non-man = 0), education (numeric), income (numeric).

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}
m1 <- lmerTest::lmer(impact_rel ~ CWV + (1|og_pid) + age + white + man + edu_num + income_num,data = df_s2_elg)

eta_table <- eta_squared(m1)
etas_for_table <- c(NA,eta_table$Eta2_partial)
apa_lm <- apa_print(m1)
table_for_print <- apa_lm$table %>% 
  mutate(eta2 = round(etas_for_table,3))

kbl(table_for_print) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Random Effects Mediation Model 1

**Predictor:** Competitive worldview.

**Mediator:** Predicted relationship impact.

**Outcome:** Dominant behavior (like the manager).

**Random effect:** Description.

**Controls:** Age, race (white = 1; non-white = 0), gender (man = 1; non-man = 0), education (numeric), income (numeric).

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}
# Step 1: Fit the mediator model
med.fit <- lme4::lmer(impact_rel ~ CWV + (1|og_pid) + age + white + man + edu_num + income_num, df_s2_elg, REML=F)

# Step 2: Fit the outcome model
out.fit <- lme4::lmer(own_likeman ~ impact_rel + CWV + (1|og_pid) + age + white + man + edu_num + income_num, df_s2_elg, REML=F)

# Step 3: Conduct the mediation analysis
med.out <- mediation::mediate(med.fit, out.fit,
                   treat = "CWV",
                   mediator = "impact_rel",
                   boot = FALSE, 
                   sims = 10000,
                   boot.ci.type="bca")

# Step 4: Create table
med_results <- data.frame(
  Effect = c("ACME (indirect)", "ADE (direct)", "Total Effect", "Prop. Mediated"),
  Estimate = round(c(med.out$d0, med.out$z0, med.out$tau.coef, med.out$n0), 3),
  `95% CI Lower` = round(c(med.out$d0.ci[1], med.out$z0.ci[1], med.out$tau.ci[1], med.out$n0.ci[1]), 3),
  `95% CI Upper` = round(c(med.out$d0.ci[2], med.out$z0.ci[2], med.out$tau.ci[2], med.out$n0.ci[2]), 3),
  `p-value` = signif(c(med.out$d0.p, med.out$z0.p, med.out$tau.p, med.out$n0.p), 3)
)

kbl(med_results) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")

```

## Random Effects Mediation Model 2

**Predictor:** Competitive worldview.

**Mediators:** Predicted relationship impact (path 1), predicted compliance impact (path 2).

**Outcome:** Dominant behavior (like the manager).

**Random effect:** Description.

**Controls:** Age, race (white = 1; non-white = 0), gender (man = 1; non-man = 0), education (numeric), income (numeric).

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}
predictor  <- "CWV"
outcome    <- "own_likeman"
mediators  <- c("impact_rel", "impact_comp")
controls   <- c("age","white","man","edu_num","income_num")
cluster_id <- "og_pid"

vars_needed <- c(outcome, predictor, mediators, controls, cluster_id)
df_cc <- df_s2_elg[complete.cases(df_s2_elg[, vars_needed]), vars_needed]

f_c <- as.formula(
  paste0(outcome, " ~ ", predictor, " + ",
         paste(controls, collapse = " + "),
         " + (1|", cluster_id, ")")
)

m_c <- lmerTest::lmer(f_c, data = df_cc)

c_row <- {
  sm <- summary(m_c)
  est <- sm$coefficients[predictor, "Estimate"]
  se  <- sm$coefficients[predictor, "Std. Error"]
  p   <- sm$coefficients[predictor, "Pr(>|t|)"]
  ci <- suppressMessages(confint(m_c, parm = predictor, method = "Wald"))
  tibble(
    label = "c",
    est = as.numeric(est),
    se  = as.numeric(se),
    ci.lower = as.numeric(ci[1]),
    ci.upper = as.numeric(ci[2]),
    pvalue = as.numeric(p)
  )
}

controls_str <- paste(controls, collapse = " + ")

model_med <- paste0(
  mediators[1], " ~ a1*", predictor, " + ", controls_str, "\n",
  mediators[2], " ~ a2*", predictor, " + ", controls_str, "\n\n",
  mediators[1], " ~~ ", mediators[2], "\n\n",
  outcome, " ~ b1*", mediators[1], " + b2*", mediators[2],
  " + c_prime*", predictor, " + ", controls_str, "\n\n",
  "ind1 := a1*b1\n",
  "ind2 := a2*b2\n",
  "ind_total := ind1 + ind2\n"
)

fit_med <- sem(
  model_med,
  data = df_cc,
  cluster = cluster_id,
  se = "robust.cluster"
)

keep_labels <- c("a1","a2","b1","b2","c_prime","ind1","ind2","ind_total")

lavaan_rows <- parameterEstimates(fit_med, ci = TRUE) %>%
  filter(label %in% keep_labels) %>%
  select(label, est, se, ci.lower, ci.upper, pvalue)


cprime_est <- lavaan_rows$est[lavaan_rows$label == "c_prime"]
indtot_est <- lavaan_rows$est[lavaan_rows$label == "ind_total"]

total_row <- c_row %>%
  mutate(label = "total")

final_table <- bind_rows(
  lavaan_rows,
  c_row,
  total_row
) %>%
  mutate(
    label = factor(
      label,
      levels = c("a1","a2","b1","b2","c","c_prime","ind1","ind2","ind_total","total")
    )
  ) %>%
  arrange(label)

kbl(final_table) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")

```