---
title: "Dominance Through the Lens of a Competitive Worldview"
subtitle: "Study 4: Analysis Report"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
knit: (function(input_file, encoding) { rmarkdown::render(input_file, encoding = encoding, output_file = 'index.html', output_dir = here::here('docs','studies','study-4')); })
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r,include=FALSE}
library(psych)
library(mediation)
library(interactions)
library(papaja)
library(kableExtra)
library(effectsize)
library(lavaan)
library(lme4)
library(tidyverse)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/dominance-in-the-competitive-jungle/main/study-4/data/"

df_s4 <- readr::read_csv(paste0(repo_url,"df_s4.csv"), show_col_types = FALSE)

set.seed(20240914)
```

```{r,include=FALSE}
df_s4 <- df_s4  %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu),
         man = ifelse(gender == "man",1,0),
         cond_num = ifelse(cond == "pos",1,0))
```


# Background

While Studies 1-3B provide correlational evidence that relationship expectancies shape dominant behavior and that worldviews, in turn, shape relationship expectancies, several important causal questions remain. In particular, is it possible to shift relationship expectancies … and would doing so change behavioral dominance? Study 4 tackles these questions by experimentally manipulating the expected relationship impact of dominant behavior and measuring its effect on incentive-compatible dominant behavior. Specifically, we posit that experimentally channeling participants’ attention to the negative, as opposed to positive, relationship consequences of dominant behavior will lead them to behave less dominantly. Additionally, we explore whether this relationship expectancy will explain the causal effect over and above compliance expectancies about the specific task and pre-existing competitive worldviews. To that end, we adapt the paradigm from Study 3A, putting participants into the manager role, and introduce a manipulation of relationship expectancies. 

# Procedure

Participants were given the same scenario, introduction, and context as the manager side of Study 3A. They were told to imagine that they were managers in a mid-sized company and that they needed to assign a task to an employee who would be randomly assigned to them. The incentive structure was identical to the one in Study 3A, with one exception: Instead of a \$2 potential bonus, the potential bonus was \$1 (for managers and employees). To motivate the employee, the manager could send one of two messages: A dominant message or a non-dominant message. After reading the scenario, incentive structure, and messages, participants were randomly assigned to one of two experimental conditions: The Positive Relationship Impact Condition or the Negative Relationship Impact Condition. Accordingly, they were asked to think and write about how the employee might react [positively/negatively] to the dominant message. Specifically, they wrote about [positive/negative] thoughts or feeling the employee could have about the manager and their relationship with them. Participants then selected which message to send and made predictions about the relationship and compliance impact of sending the dominant message. Next, they indicated the extent to which they preferred the message they selected over the other. Finally, they completed a measure of competitive worldview.
 
# Preregistered hypotheses

This study was preregistered here: <a href="https://osf.io/86me4/?view_only=d6414b68148a4dd1b87bba265095a7bf" target="_blank">Open Science Framework</a>

  1. Participants in the positive relationship impact condition, as opposed to those in the negative relationship impact condition, will be more likely to select the dominant, as opposed to non-dominant, message.
  2. Participants in the positive relationship impact condition, as opposed to those in the negative relationship impact condition, will predict more positive relationship impact of sending the dominant message.
  3. The relationship between condition and selecting the dominant message will be at least partially explained by the predicted relationship impact of sending the dominant message.
  
# Data collection

Participants were recruited through Connect by CloudResearch - an online participant pool.

```{r,echo=FALSE,results='asis',warning=FALSE,message=F}
total_n <- df_s4 %>% 
  nrow()
```

Total N = **`r total_n`**.

Responses were filtered for two quality checks: (1) a simple attention check; (2) a bot detection check.

```{r,echo=FALSE,results='asis',warning=FALSE,message=F}
df_s4_elg <- df_s4 %>% 
  filter(is_elg == 1)

eligible_n = df_s4_elg %>% 
  nrow()

df_s4 %>% 
  group_by(att_1,att_2) %>% 
  summarise(N = n()) %>% 
  arrange(desc(N)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

Eligible N = **`r eligible_n`**.

## Race/Ethnicity

```{r,results='asis',echo=TRUE,warning=FALSE,message=FALSE}
df_s4 %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4 %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4 %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4 %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
median_income_num <- df_s4_elg %>% 
  summarise(median = median(income_num,na.rm = T))

median_income <- median_income_num %>% 
  mutate(income_char = case_when(median == 1 ~ "$0-$20,000",
                                 median == 2 ~ "$20,001-$40,000",
                                 median == 3 ~ "$40,001-$60,000",
                                 median == 4 ~ "$60,001-$80,000",
                                 median == 5 ~ "$80,001-$100,000",
                                 median == 6 ~ "$100,001-$120,000",
                                 median == 7 ~ "$120,001-$140,000",
                                 median == 8 ~ "$140,001-$160,000",
                                 median == 9 ~ "$160,001-$180,000",
                                 median == 10 ~ "$180,001-$200,000",
                                 median == 11 ~ "Over $200,000")) %>% 
  select(income_char) %>% 
  unlist() %>% 
  unname()

df_s4_elg %>%
  ggplot(aes(x = income, fill = income == median_income)) +
  geom_bar(show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey66", "TRUE" = "red")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

Median income: **`r median_income`**.

# Experimental Manipulation

Depending on the condition participants were randomly assigned to, they were asked to reflect on and write about either the **positive** or **negative** relationship impact of sending the dominant message. The manipulation prompt read as follows (paste disabled; 50-character minimum):

Before you make your choice of which message you want to send, think for a moment about how your employee might react [positively/negatively] to this message:

*By now you know the task at hand. It’s time to get in there and do your absolute best across all rounds. If you don’t complete it and do it well, you will not get the full bonus.*

How and why might the employee have a **positive/negative** (or at least not **negative/positive**) reaction to that message, affecting their attitude towards the manager?

In the space below, please write 1-2 sentences about **positive/negative** thoughts or feelings they could have about the manager and their relationship with them.

## Positive Condition

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4_elg %>% 
  filter(cond == "pos") %>% 
  select(reflection) %>%
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                position = "left") %>% 
  scroll_box(width = "100%", height = "400px")

```

## Negative Condition

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4_elg %>% 
  filter(cond == "neg") %>% 
  select(reflection) %>%
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                position = "left") %>% 
  scroll_box(width = "100%", height = "400px")

```


# Measures

## Message Selection

Which of the following messages do you wish to send to your employee?

**1.** *By now you know the task at hand. It’s time to get in there and do your absolute best across all rounds. If you don’t complete it and do it well, you will not get the full bonus.*

**2.** *Your job in this task is to select the shapes that match the description. Please make sure you look at them carefully. It would be great if you can get as many of them right as possible.*

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4_elg %>% 
  group_by(message_choice) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(Perc)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Preference for dominant message

This was the message you selected: [SELECTED-MESSAGE]

To what extent did you prefer this message over the other one?

  1. Slightly preferred
  2. Moderately preferred
  3. Strongly preferred

*We later recoded this response, in combination with the message selection question, as a 6-point dominance scale (1 = Strongly preferred the non-dominant message to 6 = Strongly preferred the dominant message).*

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s4_elg %>% 
  ggplot(aes(x = pref_cont)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,6,1),
                     limits = c(0,7)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s4_elg$pref_cont,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Dominant message: Relationship expectancy

What will be the impact of this message on your employee's attitude towards you? (1 = *Extremely Negative* to 7 = *Extremely Positive*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s4_elg %>% 
  ggplot(aes(x = pred_att)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s4_elg$pred_att,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

## Dominant message: Compliance expectancy

If they choose to do the task after receiving your message, how well will they perform? Their performance can range from 0 points up to 50 points (for perfect performance).

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s4_elg %>% 
  ggplot(aes(x = pred_comp)) +
  geom_histogram(fill = "lightblue",
                 color = NA,
                 binwidth = 5) +
  scale_x_continuous(breaks = seq(0,50,5),
                     limits = c(-5,55)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_s4_elg$pred_comp,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```


## Competitive worldview

Finally, they completed the Competitive Worldview scale.

```{r,include=F}
alpha_score <- df_s4_elg %>% 
  dplyr::select(CWV_1:CWV_10R) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

1 = *Strongly Disagree* to 7 = *Strongly Agree*

  1. It’s a dog-eat-dog world where you have to be ruthless at times
  2. Life is not governed by the "survival of the fittest." We should let compassion and moral laws be our guide [R]
  3. There is really no such thing as "right" and "wrong." It all boils down to what you can get away with
  4. One of the most useful skills a person should develop is how to look someone straight in the eye and lie convincingly
  5. It is better to be loved than to be feared [R]
  6. My knowledge and experience tell me that the social world we live in is basically a competitive "jungle" in which the fittest survive and succeed, in which power, wealth, and winning are everything, and might is right
  7. Do unto others as you would have them do unto you, and never do anything unfair to someone else [R]
  8. Basically people are objects to be quietly and coolly manipulated for one’s own benefit
  9. Honesty is the best policy in all cases [R]
  10. One should give others the benefit of the doubt. Most people are trustworthy if you have faith in them [R]

R indicates a reverse-scored item.

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_s4_elg %>% 
  ggplot(aes(x = CWV)) +
  geom_density(fill = "lightblue",
                 color = NA) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(1,7)) +
  ylab("density") +
  geom_vline(xintercept = mean(df_s4_elg$CWV,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

# Analysis

## t-test 1

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4_elg <- df_s4_elg %>% 
  mutate(cond = factor(cond,levels = c("pos","neg")))

df_s4_elg %>% 
  group_by(cond) %>% 
  summarise(N = n(),
            Mean = mean(pred_att,na.rm = T),
            SD = sd(pred_att,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
m <- t.test(pred_att ~ cond,data = df_s4_elg)
d_mod <- cohens_d(m)
d = d_mod[1,1]

```

*t*(`r round(m$parameter,2)`) = `r round(m$statistic,2)`, *p* = `r round(m$p.value,3)`, *Lower CI* = `r round(m$conf.int[1],2)`, *Upper CI* = `r round(m$conf.int[2],2)`, *d* = `r round(d,2)`.

## t-test 2

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4_elg %>% 
  group_by(cond) %>% 
  summarise(N = n(),
            Mean = mean(choicedom,na.rm = T),
            SD = sd(choicedom,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
m <- t.test(choicedom ~ cond,data = df_s4_elg)
d_mod <- cohens_d(m)
d = d_mod[1,1]

```

*t*(`r round(m$parameter,2)`) = `r round(m$statistic,2)`, *p* = `r round(m$p.value,3)`, *Lower CI* = `r round(m$conf.int[1],2)`, *Upper CI* = `r round(m$conf.int[2],2)`, *d* = `r round(d,2)`.

## t-test 3

```{r,echo=TRUE,results='asis',warning=FALSE}
df_s4_elg %>% 
  group_by(cond) %>% 
  summarise(N = n(),
            Mean = mean(pref_cont,na.rm = T),
            SD = sd(pref_cont,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
m <- t.test(pref_cont ~ cond,data = df_s4_elg)
d_mod <- cohens_d(m)
d = d_mod[1,1]

```

*t*(`r round(m$parameter,2)`) = `r round(m$statistic,2)`, *p* = `r round(m$p.value,3)`, *Lower CI* = `r round(m$conf.int[1],2)`, *Upper CI* = `r round(m$conf.int[2],2)`, *d* = `r round(d,2)`.

## Mediation Model 1

Predictor: Condition (1 = positive; 0 = negative).

Mediator: Predicted relationship impact.

Outcome: Message selection (1 = dominant message; 0 = non-dominant message).

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}
# Step 1: Fit the mediator model
med.fit <- lm(pred_att ~ cond_num,
              data = df_s4_elg)

# Step 2: Fit the outcome model
out.fit <- lm(choicedom ~ cond_num + pred_att,
              data = df_s4_elg)

# Step 3: Conduct the mediation analysis
med.out <- mediation::mediate(med.fit, out.fit,
                   treat = "cond_num",
                   mediator = "pred_att",
                   boot = TRUE, sims = 10000) 

# Step 4: Create table
med_results <- data.frame(
  Effect = c("ACME (indirect)", "ADE (direct)", "Total Effect", "Prop. Mediated"),
  Estimate = round(c(med.out$d0, med.out$z0, med.out$tau.coef, med.out$n0), 3),
  `95% CI Lower` = round(c(med.out$d0.ci[1], med.out$z0.ci[1], med.out$tau.ci[1], med.out$n0.ci[1]), 3),
  `95% CI Upper` = round(c(med.out$d0.ci[2], med.out$z0.ci[2], med.out$tau.ci[2], med.out$n0.ci[2]), 3),
  `p-value` = signif(c(med.out$d0.p, med.out$z0.p, med.out$tau.p, med.out$n0.p), 3)
)

kbl(med_results) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")

```

## Mediation Model 2

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}

model <- '
  # mediator models
  pred_att ~ a1*cond_num
  pred_comp ~ a2*cond_num

  # outcome model
  choicedom ~ c*cond_num + b1*pred_att + b2*pred_comp

  # indirect effects
  ind_att := a1 * b1
  ind_comp := a2 * b2
  total := c + ind_att + ind_comp
'

fit <- sem(model, data = df_s4_elg, se = "bootstrap", bootstrap = 10000)
estimates <- parameterEstimates(fit, standardized = TRUE, ci = TRUE)
table_results <- subset(estimates, label %in% c("a1", "b1", "a2", "b2", "c", "ind_att", "ind_comp", "total"))

# Rename paths for clarity
table_results$label <- recode(table_results$label,
                              "a1" = "a1: cond → pred_att",
                              "b1" = "b1: pred_att → choicedom",
                              "a2" = "a2: cond → pred_comp",
                              "b2" = "b2: pred_comp → choicedom",
                              "c"  = "Direct effect (c')",
                              "ind_att" = "Indirect via pred_att",
                              "ind_comp" = "Indirect via pred_comp",
                              "total" = "Total effect")

# Select and rename columns
output_table <- table_results[, c("label", "est", "ci.lower", "ci.upper", "pvalue")]
names(output_table) <- c("Path", "Estimate", "95% CI Lower", "95% CI Upper", "p-value")

# Round for reporting
output_table[2:5] <- lapply(output_table[2:5], function(x) signif(x, 3))

# Print table
kbl(output_table) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")

```

## Linear Model 1

Predictor: Condition (1 = positive; 0 = negative).

Moderator: Competitive worldview.

Outcome: Message selection (1 = dominant message; 0 = non-dominant message).

```{r,echo=TRUE,results='asis',warning=FALSE,message=F,fig.align='left'}
m1 <- lm(choicedom ~ cond_num*CWV,data = df_s4_elg)

eta_table <- eta_squared(m1)
etas_for_table <- c(NA,eta_table$Eta2_partial)
apa_lm <- apa_print(m1)
table_for_print <- apa_lm$table %>% 
  mutate(eta2 = round(etas_for_table,3))

kbl(table_for_print) %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

